Chain molecules are a typical problem of statistical mechanics \cite{statisticalmechanics}.
The main mathematical approach applied to chain molecules is the statistical mechanics framework, which usually applies statistical methods and probability theory to large assemblies of microscopic entities.
In our case, the chain represent the system, and we're interested in the interaction within its parts.
If we set up the problem considering the system in a canonical ensemble, which means that it can exchange energy with the universe but matter, we can write the \emph{partition function} as
\begin{equation*}
    Z = \sum_i e^{-\beta\epsilon_i}
\end{equation*}
where $\epsilon_i$ is the energy of the $i$-th microstate and $\beta = \frac{1}{k_BT}$.
From that we can define the \emph{Helmholtz' free energy} of the system
\begin{equation*}
    F = -\frac{1}{\beta} \ln Z
\end{equation*}
and we know that the stable conformation of the chain will minimize this energy.
The consequence of that approach is that if we knew all the microstates (possible conformations of the chain) of the system and their energies, we would be able to compute all thermodynamic potentials.
Unfortunately, we are not able to compute every single microstate with its energy for long protein: the best we can do, as we will see, is to estimate the number of possible folds or try to find the global minima (solution) of the free energy.

In particular, this project will focus on the protein folding problem.
How protein folds is a vital process that can be useful for a lot of purposes, from bioengineering to the medical applications.
Understanding how proteins fold may help us to cure diseases like Alzheimer or anemia, in which proteins start to not fold correctly, treat virus infections and design more efficient drugs \cite{PERM}. 
Moreover, having a tool which allows us to simulate the folding process can be useful in order to understand what happens when a mutation occurs in a protein.
The reasons for mutations may be a lot, including the radiation exposure and the environment itself \cite{zanichelli}.
A mutation is not always a bad thing because evolution starts from them, and we may also force some mutations in laboratory in order to get a specific result.

The aim of this project is to report the main results in the developing of the HP model for protein folding.
In order to do so, we'll first illustrate what the HP model is.
Next, we will analyze two main approaches to this problem.
The first one is a \emph{brute force} approach, that allows us to understand the properties of a protein by computing all its possible configurations.
However, a brute force approach is typically the last thing one would do.
An alternative will be the Reinforcement Learning method that using the so-called \emph{Deep Neural Networks} (DNNs) it's able to find the minimum of the free energy in a tolerable amount of time.